Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-13 papers/B1555_EdgeOn/B1555_letter.tex
figures and numbers updated, not much change in text

\section{Lens Modeling}
There are several public lens modeling codes allow researchers to model strong lensed systems with most common mass models. We use glafic \citep{Oguri} to explore B1555 with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The position of lens galaxy is at $(-0.1620, -0.2401)$. Model best-fit parameters are stated as following. 
SIE: $\sigma =853 km/s, e=0.27, \theta = 105.5 \degr$. 
Exponential disk: $M_{tot}=1.48 \times 10^{10} h^{-1} M_{\odot}, e=0.84, \theta=7.4 \degr, r_e = 0.20'' $, where $e$ is ellipticity and $\theta$ is the position angle measured east of north.

The comparison of radio observation and our modeling result is in Figure 2, Table 1 \& 2.\\

\begin{figure}
\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
Exponential disk is marled by the green ellipse in residue image. We believe strong dust extinction from the disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
\end{figure}

\begin{figure}
\plotone{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2036,-0.1645)$, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}

%%table1
\begin{table}
\begin{center}
\caption{Radio Observation and Model-predicted Image Positions.\label{tbl-1}}
\begin{tabular}{lllccc}
\tableline\tableline
					&Radio	&		 & Model-predicted \\
Component &East &North &East 		&North\\ 
\tableline
A ........ &$0$    			&$0$		 			&$-0.0017$ &$+0.0022$   \\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0734$ &$+0.0456$   \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4120$ &$-0.0278$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1580$ &$-0.3608$   \\  
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.}
\end{center}
\end{table}

%%table2
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-2}}
\begin{tabular}{lllccc}
\tableline\tableline
				&Radio &Infrared  &Model-predicted\\
\tableline
A/B			&$1.8$ &					&$1.7$  \\ 
A/C 		&$2.0$ &					&$2.2$  \\
A/D			&$13.0$ &					&$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Infrared flux densities are...}
\end{center}
\end{table}

@@

\begin{thebibliography}{}
\bibitem[Oguri(2010)]{Oguri} Oguri, M. 2010, \pasj, 62, 1017
\bibitem[Marlow et al.(1999)]{Marlow} Marlow, D. R., et al. 1999, \apj, 118, 654
\end{thebibliography}

>>>>

\section{Lens Modeling}
There are several public lens modeling codes allow researchers to model strong lensed systems with most common mass models. We use glafic \citep{Oguri} to explore B1555 with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The full best-fit parameters are shown in Table 1.

The comparison of radio observation and our modeling result is in Figure 2, Table 2 \& 3.\\

\begin{figure}
\plotone{B1555_Kp.eps}
\plottwo{B1555_model.eps}{B1555_residue.eps}
\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
Exponential disk is marked by the green ellipse in residue image. We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
\end{figure}

\begin{figure}
\plotone{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{lcccccc}
%%\tableline\tableline
Model &		&		 &  \\
\tableline\tableline
SIE 	& $x$		& $y$ 		& $\sigma (km/s)$ 	& $e$	& $\theta$  \\  
		&$-0.1883$ 	&$-0.1923$	&$93.74$ 			&$0.27$	& $105.5 \degr$   \\
\tableline
Expdisk	& $x$		& $y$		& $M_{tot} (h^{-1}M_{\odot})$	& $e$	& $\theta$	& $r_e$ \\
		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.4 \degr$& $0.20 ''$  \\

\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Positions are offsets measured from component A in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}

%%table2
\begin{table}
\begin{center}
\caption{Radio Observation and Model-predicted Image Positions.\label{tbl-2}}
\begin{tabular}{lccccc}
\tableline\tableline
					&Radio	&		 & Model-predicted \\
Component &East &North &East 		&North\\ 
\tableline
A ........ &$0$    		&$0$		&$-0.0000$ &$+0.0000$   \\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$   \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$   \\  
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.}
\end{center}
\end{table}

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lllccc}
\tableline\tableline
				&Radio &Infrared  &Model-predicted\\
\tableline
A/B			&$1.8$ &$3.5$ &$1.7$  \\ 
A/C 		&$2.0$ &$1.0$ &$2.2$  \\
A/D			&$13.0$ &$5.4$ &$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
\end{center}
\end{table}

@@

\bibliographystyle{apj}
\bibliography{reference.bib}

%\begin{thebibliography}{}
%\bibitem[Oguri(2010)]{Oguri} Oguri, M. 2010, \pasj, 62, 1017
%\bibitem[Marlow et al.(1999)]{Marlow} Marlow, D. R., et al. 1999, \apj, 118, 654
%\end{thebibliography}
